Evaluating RFE across chromosomes

### 2019-08-17 Manuscript/manuscript_structured.Rmd

### Consider distance
-->

>>>>

### Consider distance

## Predicting at bp resolution

### Empirical way to determine boundary regions

####################################################################################

# Results

## Determining optimal data level characteristics for TAD boundary prediction
## Identifying top predictive annotations of TAD boundaries
## Predicting TAD boundaries at bp resolution
### Comparing distance profiles of called TAD boundaries vs predicted TAD boundaries

-->

### 2019-08-17 Scripts/comparing_predicted_boundaries_vs_called_boundaries.Rmd

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

@@

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "CTCF"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red"), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "CTCF"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red"), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "right")))
```

@@

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "RAD21"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red"), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "RAD21"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red"), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "right")))
```

@@

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "SMC3"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red"), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "SMC3"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red"), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "right")))
```

@@

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "ZNF143"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red"), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "ZNF143"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red"), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "right")))
```

@@

```{r}
chromslength <- numeric()
for(i in 1:length(chrs)){
  chromslength[i] <- max(end(all_true_bounds[which(as.character(seqnames(all_true_bounds))==tolower(chrs[i]))]),
                         end(annots.GR.f[[1]][which(as.character(seqnames(annots.GR.f[[1]]))==tolower(chrs[i]))]))
}
names(chromslength) <- tolower(chrs)

@@

>>>>

called_and_pred_17 <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR17/smote/distance/enet/called_and_pred_bound_regions.rds"))
true_bound_17 <- called_and_pred_17[[3]]
pred_bound_17 <- called_and_pred_17[[4]]
rm(called_and_pred_17)

called_and_pred_18 <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR18/smote/distance/enet/called_and_pred_bound_regions.rds"))
true_bound_18 <- called_and_pred_18[[3]]
pred_bound_18 <- called_and_pred_18[[4]]
rm(called_and_pred_18)

called_and_pred_19 <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR19/smote/distance/enet/called_and_pred_bound_regions.rds"))
true_bound_19 <- called_and_pred_19[[3]]
pred_bound_19 <- called_and_pred_19[[4]]
rm(called_and_pred_19)

called_and_pred_20 <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR20/smote/distance/enet/called_and_pred_bound_regions.rds"))
true_bound_20 <- called_and_pred_20[[3]]
pred_bound_20 <- called_and_pred_20[[4]]
rm(called_and_pred_20)

called_and_pred_21 <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR21/smote/distance/enet/called_and_pred_bound_regions.rds"))
true_bound_21 <- called_and_pred_21[[3]]
pred_bound_21 <- called_and_pred_21[[4]]
rm(called_and_pred_21)

called_and_pred_22 <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR22/smote/distance/enet/called_and_pred_bound_regions.rds"))
true_bound_22 <- called_and_pred_22[[3]]
pred_bound_22 <- called_and_pred_22[[4]]
rm(called_and_pred_22)

all_true_bounds <- GRangesList(true_bound_17,
                               true_bound_18,
                               true_bound_19,
                               true_bound_20,
                               true_bound_21,
                               true_bound_22)
all_pred_bounds <- GRangesList(pred_bound_17,
                               pred_bound_18,
                               pred_bound_19,
                               pred_bound_20,
                               pred_bound_21,
                               pred_bound_22)

all_true_bounds <- do.call("c", all_true_bounds)
all_pred_bounds <- do.call("c", all_pred_bounds)

@@

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "CTCF"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = muted("red"), 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "CTCF"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = muted("red"), 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "right")))
```

@@

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "RAD21"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = muted("red"), 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "RAD21"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = muted("red"), 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "right")))
```

@@

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "SMC3"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = muted("red"), 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "SMC3"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = muted("red"), 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "right")))
```

@@

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "ZNF143"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = muted("red"), 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat, 
                col = c("white", muted("red")), 
                heatmap_legend_param = list(title = "ZNF143"),
                row_title="Chromosomes",
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = muted("red"), 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "right")))
```

@@

```{r}
all_true_bounds <- resize(all_true_bounds, width=1,fix = "center")

chromslength <- numeric()
for(i in 1:length(chrs)){
  chromslength[i] <- max(end(all_true_bounds[which(as.character(seqnames(all_true_bounds))==tolower(chrs[i]))]),
                         end(annots.GR.f[[1]][which(as.character(seqnames(annots.GR.f[[1]]))==tolower(chrs[i]))]))
}
names(chromslength) <- tolower(chrs)

@@

### Plots v2

```{r}
pred_v_called_10_df <- data.frame(LogDist = c(#Predicted
    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1),
    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[2]]))$distance+1),
    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[3]]))$distance+1),
    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[4]]))$distance+1),

    #Called
    log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[1]]))$distance+1),
    log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[2]]))$distance+1),
    log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[3]]))$distance+1),
    log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[4]]))$distance+1)
),
Annotation = c(#Predicted
    rep("CTCF",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
    rep("RAD21",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
    rep("SMC3a",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
    rep("ZNF143",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),

    #Called
    rep("CTCF",length(log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[1]]))$distance+1))),
    rep("RAD21",length(log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[1]]))$distance+1))),
    rep("SMC3a",length(log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[1]]))$distance+1))),
    rep("ZNF143",length(log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[1]]))$distance+1)))),
BoundReg = c(#Predicted
    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),

    #Called
    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[1]]))$distance+1))),
    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[1]]))$distance+1))),
    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[1]]))$distance+1))),
    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds, annots.GR.f[[1]]))$distance+1)))))

pred_v_called_10_df$BoundReg <- factor(pred_v_called_10_df$BoundReg, levels=c("Predicted", "Called"))

ggplot(pred_v_called_10_df, aes(x=BoundReg, y = LogDist, fill=BoundReg))  + 
    facet_grid(~ Annotation) +    
    stat_boxplot(geom ='errorbar', width = 0.2) + 
    geom_boxplot(outlier.shape = NA) +
    geom_signif(test = "wilcox.test", 
                comparisons = list( c("Predicted", "Called")),
                vjust = 0,
                textsize = 4,
                size = .5,
                step_increase = .08) +
    theme_minimal()+
    theme_bw()+
    ylab("Log2 Distance to Annotation")+
    xlab("") +
    scale_fill_discrete(name="Boundary Region")+
    #guides(color=FALSE, linetype=FALSE)+
    theme(axis.text.x = element_text(size=15,
                                     angle = 45,
                                     hjust = 1),
          axis.text.y = element_text(size = 15),
          axis.title.x = element_text(size = 20),
          axis.title.y = element_text(size = 20),
          strip.text.x = element_text(size = 15),
          #panel.spacing = unit(2, "lines"),
          legend.text=element_text(size=15),
          legend.title=element_text(size=20),
          plot.title = element_text(size=20),
          legend.position = "bottom")
```

### 2019-08-17 Scripts/comparing_tad_regions_across_cl_using_vd.Rmd

@@

bounds_gm12878_5kb <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/training_testing/bounds_f.rds")
bounds_k562_5kb <- readRDS("Z:/TAD_data_analysis/K562/5kb/training_testing/bounds_f.rds")

@@

bounds_gm12878_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/bounds_f.rds")
bounds_k562_10kb <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/bounds_f.rds")

@@

bounds_gm12878_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/bounds_f.rds")
bounds_k562_25kb <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/bounds_f.rds")

@@

bounds_gm12878_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/bounds_f.rds")
bounds_k562_50kb <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/bounds_f.rds")

@@

bounds_gm12878_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/bounds_f.rds")
bounds_k562_100kb <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/bounds_f.rds")

@@

gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_5kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("5 kb", gp=gpar(fontsize=50)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_10kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("10 kb", gp=gpar(fontsize=50)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_25kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("25 kb", gp=gpar(fontsize=50)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_50kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("50 kb", gp=gpar(fontsize=50)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_100kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("100 kb", gp=gpar(fontsize=50)))
grid.newpage()

>>>>

## Function to extract boundaries

```{r}
source("C:/Users/stili/Documents/TAD_predictive_modeling/Scripts/functions_for_R_package/extract_boundaries_func.r")
```

@@

#bounds_gm12878_5kb <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/training_testing/bounds_f.rds")
#bounds_k562_5kb <- readRDS("Z:/TAD_data_analysis/K562/5kb/training_testing/bounds_f.rds")

domains <- read.table("Z:/TAD_data_analysis/GM12878/5kb/GM12878_domain_data_5000.b.txt", header=F)
bounds_gm12878_5kb <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  bounds <- extract_boundaries_func(domains.mat=domains, preprocess=TRUE, chromosome=chrs[i], resolution=5000)
  bounds_gm12878_5kb[[i]] <- bounds
}
bounds_gm12878_5kb <- do.call("c", bounds_gm12878_5kb)

domains <- read.table("Z:/TAD_data_analysis/K562/5kb/K562_domain_data_5000.b.txt", header=F)
bounds_k562_5kb <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  bounds <- extract_boundaries_func(domains.mat=domains, preprocess=TRUE, chromosome=chrs[i], resolution=5000)
  bounds_k562_5kb[[i]] <- bounds
}
bounds_k562_5kb <- do.call("c", bounds_k562_5kb)

@@

#bounds_gm12878_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/bounds_f.rds")
#bounds_k562_10kb <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/bounds_f.rds")

domains <- read.table("Z:/TAD_data_analysis/GM12878/10kb/GM12878_domain_data_10000.b.txt", header=F)
bounds_gm12878_10kb <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  bounds <- extract_boundaries_func(domains.mat=domains, preprocess=TRUE, chromosome=chrs[i], resolution=10000)
  bounds_gm12878_10kb[[i]] <- bounds
}
bounds_gm12878_10kb <- do.call("c", bounds_gm12878_10kb)

domains <- read.table("Z:/TAD_data_analysis/K562/10kb/K562_domain_data_10000.b.txt", header=F)
bounds_k562_10kb <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  bounds <- extract_boundaries_func(domains.mat=domains, preprocess=TRUE, chromosome=chrs[i], resolution=10000)
  bounds_k562_10kb[[i]] <- bounds
}
bounds_k562_10kb <- do.call("c", bounds_k562_10kb)

@@

#bounds_gm12878_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/bounds_f.rds")
#bounds_k562_25kb <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/bounds_f.rds")

domains <- read.table("Z:/TAD_data_analysis/GM12878/25kb/GM12878_domain_data_25000.b.txt", header=F)
bounds_gm12878_25kb <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  bounds <- extract_boundaries_func(domains.mat=domains, preprocess=TRUE, chromosome=chrs[i], resolution=25000)
  bounds_gm12878_25kb[[i]] <- bounds
}
bounds_gm12878_25kb <- do.call("c", bounds_gm12878_25kb)

domains <- read.table("Z:/TAD_data_analysis/K562/25kb/K562_domain_data_25000.b.txt", header=F)
bounds_k562_25kb <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  bounds <- extract_boundaries_func(domains.mat=domains, preprocess=TRUE, chromosome=chrs[i], resolution=25000)
  bounds_k562_25kb[[i]] <- bounds
}
bounds_k562_25kb <- do.call("c", bounds_k562_25kb)

@@

#bounds_gm12878_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/bounds_f.rds")
#bounds_k562_50kb <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/bounds_f.rds")

domains <- read.table("Z:/TAD_data_analysis/GM12878/50kb/GM12878_domain_data_50000.b.txt", header=F)
bounds_gm12878_50kb <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  bounds <- extract_boundaries_func(domains.mat=domains, preprocess=TRUE, chromosome=chrs[i], resolution=50000)
  bounds_gm12878_50kb[[i]] <- bounds
}
bounds_gm12878_50kb <- do.call("c", bounds_gm12878_50kb)

domains <- read.table("Z:/TAD_data_analysis/K562/50kb/K562_domain_data_50000.b.txt", header=F)
bounds_k562_50kb <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  bounds <- extract_boundaries_func(domains.mat=domains, preprocess=TRUE, chromosome=chrs[i], resolution=50000)
  bounds_k562_50kb[[i]] <- bounds
}
bounds_k562_50kb <- do.call("c", bounds_k562_50kb)

@@

#bounds_gm12878_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/bounds_f.rds")
#bounds_k562_100kb <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/bounds_f.rds")

domains <- read.table("Z:/TAD_data_analysis/GM12878/100kb/GM12878_domain_data_100000.b.txt", header=F)
bounds_gm12878_100kb <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  bounds <- extract_boundaries_func(domains.mat=domains, preprocess=TRUE, chromosome=chrs[i], resolution=100000)
  bounds_gm12878_100kb[[i]] <- bounds
}
bounds_gm12878_100kb <- do.call("c", bounds_gm12878_100kb)

domains <- read.table("Z:/TAD_data_analysis/K562/100kb/K562_domain_data_100000.b.txt", header=F)
bounds_k562_100kb <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  bounds <- extract_boundaries_func(domains.mat=domains, preprocess=TRUE, chromosome=chrs[i], resolution=100000)
  bounds_k562_100kb[[i]] <- bounds
}
bounds_k562_100kb <- do.call("c", bounds_k562_100kb)

@@

gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_5kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("5 kb", gp=gpar(fontsize=50)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_10kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("10 kb", gp=gpar(fontsize=50)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_25kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("25 kb", gp=gpar(fontsize=50)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_50kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("50 kb", gp=gpar(fontsize=50)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_100kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("100 kb", gp=gpar(fontsize=50)))

### 2019-08-17 Scripts/evaluating_rfe_across_chromosomes.Rmd

ggplot(rfeperchr_summ, aes(x=Variables, y=AveMCC, color=CL)) + 
    geom_errorbar(aes(ymin=AveMCC-AveMCCSD, ymax=AveMCC+AveMCCSD), 
                  width=2, 
                  position=position_dodge(2),
                  size=1) +
    geom_line(position=position_dodge(2), size=1) +
    geom_point(position=position_dodge(2), size=2) +
    xlab("Number of top ranked annotations") +
    ylab("Cross-Validated MCC") +
    #ylim(.3,.8)+
    scale_color_discrete(name="Cell line")+
    scale_x_continuous(breaks = c(2,4,8,16,32,52),
                     labels = c(2,4,8,16,32,52))+
    theme_minimal() +
    theme_bw()+
    theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")
```

@@

rfegm12878 <- rfeperchr[which(rfeperchr$CL=="GM12878"),]
rfegm12878 <- reshape(rfegm12878[,c(1,2,4)], idvar = "Feature", timevar = "Chromosome", direction = "wide")
names(rfegm12878)[-1] <- paste0("CHR", c(1:8,10:22)) 
rfegm12878.mat <- as.matrix(rfegm12878[,-1])
rownames(rfegm12878.mat) <- rfegm12878$Feature
rfegm12878.mat[is.na(rfegm12878.mat)] <- 0
rfegm12878.mat <- apply(rfegm12878.mat,2,rev)

#using heatmap.2
distance.col = dist(rfegm12878.mat, method = "euclidean")
cluster.col = hclust(distance.col, method = "average")
my_palette <- colorRampPalette(c("white", "pink", "red"))(rcol(rfegm12878.mat))
heatmap.2(t(rfegm12878.mat),
          #labRow=rownames(rfegm12878.mat),
          #labCol=colnames(rfegm12878.mat),
          #cellnote = ,  # same data set for cell labels
          #main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins=c(12,8),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #keysize = 1.5,
          #key.title = "Elastic-Net Coefficient",
          dendrogram="column",     # only draw a row dendrogram,
          Rowv = FALSE,
          Colv = reorder(as.dendrogram(cluster.col), 37:1),
          cexRow=1.5,
          cexCol=1.5,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          rowsep=0:nrow(t(rfegm12878.mat)),
          colsep=0:ncol(t(rfegm12878.mat)),
          sepwidth=c(0.001,0.001),
          sepcolor="black"
) 
```

>>>>

ggplot(rfeperchr_summ, aes(x=Variables, y=AveMCC, color=CL)) + 
    geom_errorbar(aes(ymin=AveMCC-AveMCCSD, ymax=AveMCC+AveMCCSD), 
                  width=2, 
                  position=position_dodge(2),
                  size=1) +
    geom_line(position=position_dodge(2), size=1) +
    geom_point(position=position_dodge(2), size=2) +
    xlab("Number of top ranked annotations") +
    ylab("Cross-Validated MCC") +
    #ylim(.3,.8)+
    scale_color_discrete(name="Cell line")+
    scale_x_continuous(breaks = c(2,4,8,16,32,52),
                     labels = c(2,4,8,16,32,52))+
    theme_minimal() +
    theme_bw()+
    theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")
```

@@

#gm12878
rfegm12878 <- rfeperchr[which(rfeperchr$CL=="GM12878"),]
rfegm12878 <- reshape(rfegm12878[,c(1,2,4)], idvar = "Feature", timevar = "Chromosome", direction = "wide")
names(rfegm12878)[-1] <- paste0("CHR", c(1:8,10:22)) 
rfegm12878.mat <- as.matrix(rfegm12878[,-1])
rownames(rfegm12878.mat) <- rfegm12878$Feature
rfegm12878.mat[is.na(rfegm12878.mat)] <- 0
rfegm12878.mat <- apply(rfegm12878.mat,2,rev)

#using heatmap.2
distance.col = dist(rfegm12878.mat, method = "euclidean")
cluster.col = hclust(distance.col, method = "average")
my_palette <- colorRampPalette(c("white", "pink", "red"))(ncol(rfegm12878.mat))
heatmap.2(t(rfegm12878.mat),
          #labRow=rownames(rfegm12878.mat),
          #labCol=colnames(rfegm12878.mat),
          #cellnote = ,  # same data set for cell labels
          #main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins=c(12,8),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=FALSE,
          #keysize = 1.5,
          #key.title = "Elastic-Net Coefficient",
          dendrogram="column",     # only draw a row dendrogram,
          Rowv = FALSE,
          Colv = reorder(as.dendrogram(cluster.col), 37:1),
          cexRow=1.5,
          cexCol=1.5,
          #labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          rowsep=0:nrow(t(rfegm12878.mat)),
          colsep=0:ncol(t(rfegm12878.mat)),
          sepwidth=c(0.001,0.001),
          sepcolor="black"
) 
```
